%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
% !TeX spellcheck = en
\documentclass{resume} % Use the custom resume.cls style
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=cyan,      
    urlcolor=cyan,
}
 
\urlstyle{same}

\usepackage[left=0.75in,top=1in,right=0.75in,bottom=1in]{geometry} % Document margins
\usepackage[colorlinks=true, linkcolor=black, urlcolor=black]{hyperref}
\usepackage{marvosym}
\usepackage{graphicx}

\name{Amar Kumar Sinha}
\address{\href{mailto:amarkrsinha1997@gmail.com}{amarkrsinha1997@gmail.com} \\
         \href{https://www.linkedin.com/in/amar-sinha-5530b1158/}{in/amar-sinha} \\
         \href{https://github.com/amarkrsinha1997/}{github.com/amarkrsinha1997} \\
         \href{tel:+917002879316}{+917002879316}}

\begin{document}

%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Summary}
  \begin{rSummarySection}
  {
    \item 3+ years of experience in Front-end and 1-year experience in Back-end Development with hands-on in designing the scalable system with future needs in mind, automated test-suite, security, communicating with stakeholders to deliver the feature, mock base development, CI/CD pipeline.
  }
  \end{rSummarySection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILL SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}
  \begin{rSummarySection}
  {
    \item {\it JavaScript/TypeScript/Python, ReactNative/ReactJS/VueJS/NextJS,} 
    \item {\it GraphQL, Redux, HTML/CSS/Animation, Web-Components,}
    \item {\it Flask/Django/NodeJS, MySQL/MongoDB/MariaDB, Docker, Nginx,}
    \item {\it PWA, Mirco-Frontend, Design Pattern, WebSockets, TDD, Micro-Service, MVC.}
  }
  \end{rSummarySection}
\end{rSection}

%----------------------------------------------------------------------------------------
% WORK SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

  \begin{rWorkSection}{\Large Udaan}
                     {Bangalore, India}
                     {Application Developer II}
                     {Apr'21 -- Present} {
    \href{https://udaan.com}{Udaan B2B Platform for Indian Retailers}
    \item Decreased the cost of invoicing generation by building in-house PDF library and migrating all the PDF to use it which decrease the cost directly by 90-95\%
    \item Migrated legacy screens to using the latest in-house built library which works on all web & mobile.
    \item Built pages in internal application which support team use to resolve customers query/issue.
    \item Accommodate most of the Compliance/Tax changes by Government of.India into App and Invoicing System
  }
  \end{rWorkSection}
  \begin{rWorkSection}{\Large ThoughtWorks}
                     {Bangalore, India}
                     {Application Developer I}
                     {June'19 -- Apr'21} {
    {\it\bf Worked on E-commerce platform:} \href{https://www.sodimac.cl/sodimac-cl/}{Sodimac Chile}, \href{https://www.falabella.com/falabella-cl/}{Falabella Chile},  \href{https://www.sodimac.com.pe/sodimac-pe/}{Sodimac Peru}.
    \item Worked on multiple features like Invoice PDF Generator, Order List/Details/Tracking, Product Repurchase, Shipping And Cart Page, Registration/Profile/Add-Edit Address Forms with Google Map API \& 100\% test coverage, covering all the possible scenarios.
    \item Abstracted Login/Social-Login/Logout/Login-Verifying logic in internal libraries by building Login-SDK and published it on NPM(Private).
    \item Prevented SQL injection in the Application by writing validations in gateway service.
    \item Extended Application for an entire new tenant by creating feature toggle and updated the existing components to support feature configuration.
  }
  \end{rWorkSection}

  \begin{rWorkSection}{\Large NavGurukul}
                     {Bangalore, India}
                     {Software Engineer}
                     {Apr'18 -- Jun'19} {
    {\it\bf Worked on} \href{https://saral.navgurukul.org/}{E-Learning Platform} {\it\bf and} \href{http://admissions.navgurukul.org/}{Admission Management Portal}. 
    \item Decreased the query time by increasing use of indexes and parallel queries.
    \item Increased Admission of students by creating a \href{https://github.com/amarkrsinha1997/question-pdf-generator}{PDF generator} that generates different sets of question paper using random questions from DB.
    \item Built API to extract CSV and build new one's, process marks based on answers of students.
    \item Integrated Google Sheet with Application to update the real-time data of students.
    \item Decrease the UI load time by converting Application into SSR using NextJS.
  }
  \end{rWorkSection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}
  \begin{rProjectSection}
    \item \textbf {AtomicDesign} -- Login form built using Atomic Design, StoryBook.
    \href{https://github.com/amarkrsinha1997/atomic-design}{React Repo}
    \item \textbf {ReactGram} -- React App built using MVC pattern, TDD.
    \href{https://github.com/amarkrsinha1997/reactgram}{React, RTL}
    \item \textbf {File transfer utility} -- Secure file transfer utility built using web-sockets. \href{https://github.com/amarkrsinha1997/secure-filetransfer}{Sockets, Flask}
    \item \textbf {Examination Platform} -- Open Source Project for taking online MCQ Exams. \href{https://github.com/amarkrsinha1997/MCQ-Testing-Platform}{Flask}
    \item \textbf {Decision Tree, ML} -- ML program to build decision tree \href{https://github.com/amarkrsinha1997/ml-university-exercise}{Numpy}
    \item \textbf {Live Scrapper} -- Live tennis tournament scrapper. \href{https://github.com/amarkrsinha1997/tennis-live-data-scrapper}{Selenium}
  \end{rProjectSection}

%   \begin{rBlurbSection}
%     \item {\em Open-source contributions:}
%       I am an active OSS contributor. My \href{http://bit.ly/2kdr9Ui}{\textbf{Merged PR's}} and \href{http://bit.ly/2kxjvV9}{\textbf{open PR's}}.
%   \end{rBlurbSection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	Certificate Section
%----------------------------------------------------------------------------------------

% \begin{rSection}{Certificates}
%   \begin{rProjectSection}
%     \item \textbf {Certified Kubernetes Administrator (CKA)} -- \href{https://www.youracclaim.com/badges/e93b0ba2-51ea-41b3-82ba-10cf4d67ac70}{Validity: December 2020 to December 2023}.  
%   \end{rProjectSection}
% \end{rSection}

%----------------------------------------------------------------------------------------
%	Talks Section
%----------------------------------------------------------------------------------------

\begin{rSection}{Other Experience}
  \begin{rProjectSection}
    \item \textbf {Mentoring Students \& Curriculum Development (NavGurukul)} -- Identified students roadblocks \& core problems in learning, facilitated problem solving, innovated different methods to teach programming. Developed tech curriculum for underprivileged kids to teach them coding.
    
    \item \textbf {Student Admissions Interview (NavGurukul)} -- Interviewed 100+ students interested in joining NavGurukul. I learned to patiently talk to strangers and interview them for admission.
    
    \item \textbf {Training \& Placement coordinator (NavGurukul)} -- Worked with the founders to find incrementally better ways to build a learning environment for students.
    Facilitated resume preparations, applying for jobs \& preparing for interviews.
  \end{rProjectSection}
\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
  \begin{rEducationSection}{IGNOU, Delhi}
                          {Dec '20 -- Present}
                          {Bachelor of Computer Application}
  \end{rEducationSection}
  \begin{rEducationSection}{NavGurukul, Bangalore}
                          {Nov '17 -- Apr '18 }
                          {Diploma of Computer Application}
  \end{rEducationSection}
  \begin{rEducationSection}{AryaVidyaPeeth, Guwahati}
                          {Jun '14 -- Apr '16 }
                          {Higher Secondary in Science}
  \end{rEducationSection}
\end{rSection}

\end{document}
